---
title: "Fucking Map""
---

Load all the necessary libraries
```{r}
library(ggmap)
library(mapproj)
library(ggplot2)
library(maptools)
library(rgdal)
library(rgeos)
library(foreign) # needed for read.dbf()
library(doBy) #needed for the county name portion 
```

Read the shapefile and put the info in a dataframe
```{r}
# read administrative boundaries                              
setwd("/Users/gustavogrinsteins/Lehigh/CSE160/HW12")

#New method to change the projection (Geographical coordinates)
Mapito <- readOGR("Counties.shp", layer = "Counties")

#(Change it to what google maps uses)
correctMapito <- spTransform(Mapito, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))

# extract sequence of points and assign IDs to states
myMapDf <- fortify(correctMapito)

# interpret id variable as integer
myMapDf$id <- as.numeric(myMapDf$id)
```

Read the detailed file with the info of each county and get rid of extra stuff

```{r}
db <- read.dbf("Counties.dbf")
db$ID <- as.integer(rownames(db))-1
```

Plotting the raster image
```{r}
#Graphing the information
map <- get_map(location = "NY", zoom = 6)
#Start the google map figure (raster)
m0 <- ggmap(map) + xlim(-80,-71) + ylim(40,45.5)
m0
```

Plotting the shaded states by id

```{r}
m1 <- m0 + geom_polygon(aes(x=long, y=lat, group=group, fill=id), data=myMapDf, alpha=.7) + scale_fill_gradient(low="red", high="green")
m1
```

Adding the county's borders

```{r}
m2 <- m1 + geom_path(aes(x=long, y=lat, group=group), data=myMapDf, color='black')
m2
```

Adding the county name

```{r}
#This line gets all the id's and gives them coordinates
txtVal <- summaryBy(long + lat ~ id, data=myMapDf, FUN=mean, keep.names=T)
#This lines plots the text for each county name
m3 <- m2 + geom_text(aes(x=long, y=lat, label=db[id+1,"NAME"]), data=txtVal, col="yellow", cex=2)
m3
```

Obtain the income data
```{r}
#Getting median income info into db
#Had to change St. Lawrence to St Lawrence
householdIncome <- read.csv("/Users/gustavogrinsteins/Lehigh/CSE160/MedianHousholdIncome.csv", header=TRUE)
#Clean Houshold Income
householdIncome$Rank <- NULL
#Insert this information in db
CountyIncome <- merge(db, householdIncome, by.x="NAME", by.y="County")
#Change the type of the income object
CountyIncome$MedianHouseholdIncome <- as.numeric(CountyIncome$Median)
```


Merge this data into our plotting dataframe
```{r}
#Add the values to out plotting dataframe do not merge the data
myMapDf <- merge(myMapDf, CountyIncome, by.x="id", by.y="ID", sort = FALSE)
```

Plot the shades according to the info
```{r}
#Graphing the information
map <- get_map(location = "NY", zoom = 6)
#Start the google map figure (raster)
m0 <- ggmap(map) + xlim(-80,-71) + ylim(40,45.5)

#Putting the shades
m1 <- m0 + geom_polygon(aes(x=long, y=lat, group=group, fill=MedianHouseholdIncome), data=myMapDf, alpha=.7) + scale_fill_gradient(low="red", high="green")

#Adding county's borders
m2 <- m1 + geom_path(aes(x=long, y=lat, group=group), data=myMapDf, color='black')

#Adding text values
#This line gets all the id's and gives them coordinates
txtVal <- summaryBy(long + lat ~ id, data=myMapDf, FUN=mean, keep.names=T)
#This lines plots the text for each county name
m3 <- m2 + geom_text(aes(x=long, y=lat, label=db[id+1,"NAME"]), data=txtVal, col="yellow", cex=2)

m3
```


